### 2019-07-10 2-Chapters/3-Chapter/SMPyBandits_paper.git/longpaper.tex
Vérifications grâce à emccabedj.ucc.asn.au/checktex.html, avant intégration des commentaires d'Emilie sur ma conclusion

For example, this short bash snippet \footnote{See
  \href{https://smpybandits.github.io/How_to_run_the_code.html}{this
  page of the documentation} for more details.} shows how to clone the
code, install the requirements for Python 3 (in a virtualenv
{[}@virtualenv{]}), and starts some simulation for \(N=1000\)
repetitions of the default non-Bayesian Bernoulli-distributed problem,
for \(K=9\) arms, an horizon of \(T=10000\) and on \(4\) CPUs \footnote{It
  takes about \(20\) to \(40\) minutes for each simulation, on a
  standard \(4\)-cores \(64\) bits GNU/Linux laptop.}. Using environment
variables (\texttt{N=1000}) when launching the simulation is not
required but it is convenient.

@@

\begin{itemize}
\tightlist
\item
  In {[}@Besson2018c{]}, we used \emph{SMPyBandits} to illustrate and
  compare different ``doubling trick'' schemes \footnote{More details
    and illustrations are given on the documentation page,
    \href{https://smpybandits.github.io/DoublingTrick.html}{\texttt{DoublingTrick}}.}.
  In sequential learning, an algorithm is \emph{anytime} if it does not
  need to know the horizon \(T\) of the experiments. A well-known trick
  for transforming any non-anytime algorithm to an anytime variant is
  the ``Doubling Trick'': start with an horizon \(T_0\in\mathbb{N}\),
  and when \(t > T_i\), use \(T_{i+1} = 2 T_i\). We studied two generic
  sequences of growing horizons (geometric and exponential), and we
  proved two theorems that generalized previous results. A geometric
  sequence suffices to minimax regret bounds (in
  \(R_T = \mathcal{O}(\sqrt(T))\)), with a constant multiplicative loss
  \(\ell \leq 4\), but cannot be used to conserve a logarithmic regret
  bound (in \(R_T = \mathcal{O}(\log(T))\)). And an exponential sequence
  can be used to conserve logarithmic bounds, with a constant
  multiplicative loss also \(\ell \leq 4\) in the usual setting. It is
  still an open question to know if a well-tuned exponential sequence
  can conserve minimax bounds or weak minimax bounds (in
  \(R_T = \mathcal{O}(\sqrt{T \log(T)})\)).
\end{itemize}

>>>>

For example, this short bash snippet \footnote{See
  \href{https://smpybandits.github.io/How_to_run_the_code.html}{this
  page of the documentation} for more details.} shows how to clone the
code, install the requirements for Python 3 (in a virtualenv
{[}@virtualenv{]}), and starts some simulation for \(N=1000\)
repetitions of the default non-Bayesian Bernoulli-distributed problem,
for \(K=9\) arms, a horizon of \(T=10000\) and on \(4\) CPUs \footnote{It
  takes about \(20\) to \(40\) minutes for each simulation, on a
  standard \(4\)-cores \(64\) bits GNU/Linux laptop.}. Using environment
variables (\texttt{N=1000}) when launching the simulation is not
required but it is convenient.

@@

\begin{itemize}
\tightlist
\item
  In {[}@Besson2018c{]}, we used \emph{SMPyBandits} to illustrate and
  compare different ``doubling trick'' schemes \footnote{More details
    and illustrations are given on the documentation page,
    \href{https://smpybandits.github.io/DoublingTrick.html}{\texttt{DoublingTrick}}.}.
  In sequential learning, an algorithm is \emph{anytime} if it does not
  need to know the horizon \(T\) of the experiments. A well-known trick
  for transforming any non-anytime algorithm to an anytime variant is
  the ``Doubling Trick'': start with a horizon \(T_0\in\mathbb{N}\),
  and when \(t > T_i\), use \(T_{i+1} = 2 T_i\). We studied two generic
  sequences of growing horizons (geometric and exponential), and we
  proved two theorems that generalized previous results. A geometric
  sequence suffices to minimax regret bounds (in
  \(R_T = \mathcal{O}(\sqrt(T))\)), with a constant multiplicative loss
  \(\ell \leq 4\), but cannot be used to conserve a logarithmic regret
  bound (in \(R_T = \mathcal{O}(\log(T))\)). And an exponential sequence
  can be used to conserve logarithmic bounds, with a constant
  multiplicative loss also \(\ell \leq 4\) in the usual setting. It is
  still an open question to know if a well-tuned exponential sequence
  can conserve minimax bounds or weak minimax bounds (in
  \(R_T = \mathcal{O}(\sqrt{T \log(T)})\)).
\end{itemize}

### 2019-07-10 2-Chapters/3-Chapter/SMPyBandits_paper.git/paper.tex
Done changing notations \{1,\dots,M\} -> [M] all over the PhD
Vérifications grâce à emccabedj.ucc.asn.au/checktex.html, avant intégration des commentaires d'Emilie sur ma conclusion

More formally, a stochastic MAB is defined by $K>1$ distributions $\nu_k$ (arms),
and \emph{i.i.d.} rewards $r_k(t) \sim \nu_k, \forall t$.
An agent choose arm $A(t)\in\{1,\dots,K\}$ at time $t$ and
observes the reward $r_{A(t)}(t)$ without knowing the other (hidden) rewards.
Her goal is to maximize $\sum_{t=1}^T r_{A(t)}(t)$ by sequentially exploring the $K$ arms,
and she essentially has to find and exploit the best one as fast as possible.
This library tackles one dimensional distributions,
and supports \href{https://SMPyBandits.GitHub.io/docs/Arms.Bernoulli.html}{\texttt{Bernoulli}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Binomial.html}{\texttt{binomial}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Poisson.html}{\texttt{Poisson}}, and a generic \href{https://SMPyBandits.GitHub.io/docs/Arms.DiscreteArm.html}{\texttt{discrete}} distributions,
as well as \href{https://SMPyBandits.GitHub.io/docs/Arms.Exponential.html}{\texttt{exponential}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Gamma.html}{\texttt{gamma}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Gaussian.html}{\texttt{Gaussian}} (of known scale or variance) and \href{https://SMPyBandits.GitHub.io/docs/Arms.Uniform.html}{\texttt{uniform}} continuous distributions,
which can be truncated to an interval $[a,b]$ or have unbounded support ($\mathbb{R}$).

@@

Launching simulations is easy, for instance this snippet shows how to
start \(N=1000\) repetitions of a simple non-Bayesian
Bernoulli-distributed problem, for \(K=9\) arms, an horizon of
\(T=10000\) and on \(4\) CPUs. Such simulation takes about \(20\) minutes, on a standard \(4\)-cores \(64\) bits GNU/Linux
laptop. Using environment variables (\texttt{N=1000} etc) in the command
line is not required, but it is convenient:

@@

\begin{itemize}
\tightlist
\item
  In \citet{Besson2018DoublingTricks}, we used \emph{SMPyBandits} to illustrate and
  compare different ``doubling trick'' schemes\footnote{See the
    page
    \href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{\texttt{SMPyBandits.GitHub.io/DoublingTrick}}
    on the documentation.}. In sequential learning, an algorithm is
  \emph{anytime} if it does not need to know the horizon \(T\) of the
  experiments. A well-known trick for transforming any non-anytime
  algorithm to an anytime variant is the ``Doubling Trick'': start with
  an horizon \(T_0\in\mathbb{N}^*\), and when \(t > T_i\), use
  \(T_{i+1} = 2 T_i\). We studied two generic sequences of growing
  horizons (geometric and exponential), and we proved two theorems that
  generalized previous results. A geometric sequence suffices to conserve minimax
  regret bounds (in \(R_T = \mathcal{O}(\sqrt{T})\)), with a constant
  multiplicative loss \(\ell \leq 4\), but cannot be used to conserve a
  logarithmic regret bound (in \(R_T = \mathcal{O}(\log(T))\)). And an
  exponential sequence can be used to conserve logarithmic bounds, with
  a constant multiplicative loss also \(\ell \leq 4\) in the usual
  setting. It is still an open question to know if a well-tuned
  exponential sequence can conserve minimax bounds, or even ``weak'' minimax
  bounds (in \(R_T = \mathcal{O}(\sqrt{T \log(T)})\)).
\end{itemize}

>>>>

More formally, a stochastic MAB is defined by $K>1$ distributions $\nu_k$ (arms),
and \emph{i.i.d.} rewards $r_k(t) \sim \nu_k, \forall t$.
An agent choose arm $A(t)\in[K]$ at time $t$ and
observes the reward $r_{A(t)}(t)$ without knowing the other (hidden) rewards.
Her goal is to maximize $\sum_{t=1}^T r_{A(t)}(t)$ by sequentially exploring the $K$ arms,
and she essentially has to find and exploit the best one as fast as possible.
This library tackles one dimensional distributions,
and supports \href{https://SMPyBandits.GitHub.io/docs/Arms.Bernoulli.html}{\texttt{Bernoulli}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Binomial.html}{\texttt{binomial}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Poisson.html}{\texttt{Poisson}}, and a generic \href{https://SMPyBandits.GitHub.io/docs/Arms.DiscreteArm.html}{\texttt{discrete}} distributions,
as well as \href{https://SMPyBandits.GitHub.io/docs/Arms.Exponential.html}{\texttt{exponential}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Gamma.html}{\texttt{gamma}}, \href{https://SMPyBandits.GitHub.io/docs/Arms.Gaussian.html}{\texttt{Gaussian}} (of known scale or variance) and \href{https://SMPyBandits.GitHub.io/docs/Arms.Uniform.html}{\texttt{uniform}} continuous distributions,
which can be truncated to an interval $[a,b]$ or have unbounded support ($\mathbb{R}$).

@@

Launching simulations is easy, for instance this snippet shows how to
start \(N=1000\) repetitions of a simple non-Bayesian
Bernoulli-distributed problem, for \(K=9\) arms, a horizon of
\(T=10000\) and on \(4\) CPUs. Such simulation takes about \(20\) minutes, on a standard \(4\)-cores \(64\) bits GNU/Linux
laptop. Using environment variables (\texttt{N=1000} etc) in the command
line is not required, but it is convenient:

@@

\begin{itemize}
\tightlist
\item
  In \citet{Besson2018DoublingTricks}, we used \emph{SMPyBandits} to illustrate and
  compare different ``doubling trick'' schemes\footnote{See the
    page
    \href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{\texttt{SMPyBandits.GitHub.io/DoublingTrick}}
    on the documentation.}. In sequential learning, an algorithm is
  \emph{anytime} if it does not need to know the horizon \(T\) of the
  experiments. A well-known trick for transforming any non-anytime
  algorithm to an anytime variant is the ``Doubling Trick'': start with
  a horizon \(T_0\in\mathbb{N}^*\), and when \(t > T_i\), use
  \(T_{i+1} = 2 T_i\). We studied two generic sequences of growing
  horizons (geometric and exponential), and we proved two theorems that
  generalized previous results. A geometric sequence suffices to conserve minimax
  regret bounds (in \(R_T = \mathcal{O}(\sqrt{T})\)), with a constant
  multiplicative loss \(\ell \leq 4\), but cannot be used to conserve a
  logarithmic regret bound (in \(R_T = \mathcal{O}(\log(T))\)). And an
  exponential sequence can be used to conserve logarithmic bounds, with
  a constant multiplicative loss also \(\ell \leq 4\) in the usual
  setting. It is still an open question to know if a well-tuned
  exponential sequence can conserve minimax bounds, or even ``weak'' minimax
  bounds (in \(R_T = \mathcal{O}(\sqrt{T \log(T)})\)).
\end{itemize}

### 2019-07-10 2-Chapters/3-Chapter/chapter3.tex
Vérifications grâce à emccabedj.ucc.asn.au/checktex.html, avant intégration des commentaires d'Emilie sur ma conclusion

\paragraph{References.}
%
The code for \SMPyBandits{} is hosted at \texttt{\href{https://GitHub.com/SMPyBandits/SMPyBandits/}{GitHub.com/SMPyBandits/SMPyBandits}}, its documentation is at \texttt{\href{https://SMPyBandits.GitHub.io/}{SMPyBandits.GitHub.io}}, and all the library is freely publicly released under the MIT open-source License.
This chapter is based on the article \cite{SMPyBanditsJMLR}.

@@

\paragraph{Simulation loop for single-player MAB.}
%
Any simulation library targeting single-player bandit problems must implement at least three components:
reward distributions, MAB algorithms, and a simulation loop that essentially looks like this.
% \begin{itemize}
    % \item
    First, initialize the MAB problem and one or more algorithms,
    % \item
    Then, for $t=1$ to $t=T$ (known before hand), repeat the following block (for each algorithm). Ask algorithm $\cA$ her chosen arm $A(t)$, then sample a (random) reward $r(t)$ (\iid) from distribution $\nu_{A(t)}$, and finally feeds the observation $(A(t), r(t))$ to the algorithm.
    % \item
    At the end, compute the cumulated reward, the regret, then plot visualizations etc.
% \end{itemize}
%
Note that the second step should be repeated a large number of times (\eg, $N=100$), in order to study \emph{mean} regret and not only the regret in one single trajectory.
If one wants to compare algorithms on a same problem, it is possible to sample all the rewards $(Y_{k,t})_{k\in[K], t\in[T]}$ before-hand, and store them so that for each repetition of the simulation, the randomness from the environment (\ie, the rewards) has the same impact on all the algorithms (with the option \texttt{configuration["cache\_reward"] = True}).

@@

Any simulation library targeting multi-players bandit problems must implement at least another component:
% a collision model, and
a simulation loop that essentially looks like this.
% \begin{itemize}
    % \item
    First, initialize the MAB problem with $M$ players, and one or more cohorts of $M$ players (one player is one algorithm, usually $M$ times the same one),
    % \item
    For $t=1$ to $t=T$ (known before hand), repeat the following block (for each cohort). Ask each player $\cA^j$ her chosen arm $A^j(t)$, then query the collision model to know which player will get a zero reward (for a collision) and which player will get a random reward from the environment.
    Then, sample (random) feedback $Y_{k,t}$ (\iid) from distributions $\nu_{k}$, and compute the rewards $r^j(t)$ from the random feedback using the collision model.
    Finally, feed the observation $(A^j(t), Y_{A^j(t),t}, r^j(t))$ to player $j$, for all the $M$ players,
    %
    The default collision model is the most widely studied in the literature, where a player encounters a collision (\ie, received a zero reward $r^j(t)=0$) if she is not the only one to have chosen an arm $k=A^j(t)$, otherwise $r^j(t)=Y_{A^j(t),t}$ if she is the only one playing this arm.
    % \item
    At the end, compute the accumulated reward, the regret, then plot visualizations etc.
% \end{itemize}

@@

gaussian_problem = MAB({'arm_type': Gaussian, 'params': means})
gaussian_problem.plotHistogram()  # display the histogram shown below
    \end{minted}
    \caption{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, a plot a histogram of rewards, with \SMPyBandits.}
    % \captionof{listing}{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, a plot a histogram of rewards, with SMPyBandits. \label{lst:3:pythonCodeCreateProblem}}
    \label{lst:3:pythonCodeCreateProblem}
\end{listing}
\end{small}

@@

Simulations are easily executed, \eg, Code~\ref{lst:3:howToRunBasicLibrary} shows how to start $N=1000$ repetitions of a simple non-Bayesian Bernoulli-distributed problem, for $K=9$ arms, an horizon of $T=10000$ and on $4$ CPU.
It takes about $20$ min, on a $4$-core $64$-bit GNU/Linux laptop.
Environment variables (\texttt{N=1000} etc) in the command line are not required, but they are convenient.

@@

\paragraph{Travis CI.}
Since $2018$, we use the free web service provided by Travis CI (\href{https://travis-ci.org/}{\texttt{Travis-CI.org}}).
It allows to automatically run short numerical simulations after every commit,
in order to check that each modification on any part of the codebase does not break anything, as well as giving an up-to-date example of log files that shows online the results of different examples of experiments. The tests covers all the main models and almost all the algorithms implemented in \SMPyBandits, and it has been proven very useful to quickly find and fix new bugs.
For more details, see \href{https://travis-ci.org/SMPyBandits/SMPyBandits}{\texttt{Travis-CI.org/SMPyBandits/SMPyBandits}}.
%
Since its first use, the service did about $190$ builds, and about $30\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.travis.yml} file in \SMPyBandits{} main folder, and it runs numerical experiments with a short horizon (\eg, $T=100$) and a small number of repetitions (\ie, $N=4$), but covering all the different models implemented by \SMPyBandits{} (and even including some that are not covered in this chapter, like the Markov model, or the sparse multi-players model).
Builds typically run for $15$ minutes, and Travis CI have been proven to be very useful in our development process.

@@

    \item
In \cite{Besson2018DoublingTricks}, we used \SMPyBandits{} to illustrate and compare different "doubling trick" schemes.
\texttt{\href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{SMPyBandits.GitHub.io/DoublingTrick.html}}
% (see Appendix~\ref{app:2:DoublingTricks})
% In sequential learning, an algorithm is said to be ``anytime'' if it does not need to know the horizon $T$ of the experiments. A well-known trick for transforming any ``non-anytime'' algorithm to an ``anytime'' variant is the ``Doubling Trick'': start with an horizon $T_0\in\mathbb{N}^*$, and when $t > T_i$, use $T_{i+1} = 2 T_i$. We studied two generic sequences of growing horizons (geometric and exponential), and we proved two theorems that generalized previous results. A geometric sequence suffices to keep minimax regret bounds (in $R_T = \mathcal{O}(\sqrt{T})$), with a constant multiplicative loss $\ell \leq 4$, but cannot be used to keep a logarithmic regret bound (in $R_T = \mathcal{O}(\log(T))$). And an exponential sequence can be used to keep logarithmic bounds, with a constant multiplicative loss also $\ell \leq 4$ in the usual setting. It is still an open question to know if a well-tuned exponential sequence can keep minimax bounds, or "weak" minimax bounds (in $R_T = \mathcal{O}(\sqrt{T \log(T)})$).

@@

    \item
    % Algorithm 13 is
    Anytime variant of \KLUCBswitch{} from \cite{GarivierHadiji2018}
    (\texttt{klUCBswitchAnytime}),
    is a very recent variant of \KLUCB{} \cite{KLUCBJournal}.
    It mimics the \KLUCB{} algorithm but uses a much more complicated function to compute the upper confidence bounds, and uses more storage.
    It is anytime, and was prove to obtain good ``best of both world'' performances, meaning that it achieves an asymptotically optimal $\cO(\log(T))$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.
    Empirically, it usually outperforms (slightly) \klUCB{} in terms of regret, and costs about the same memory, but it is slower.

    \item
    % Algorithm 14 is
    \textsc{Tsallis-Inf} from \cite{Zimmert2018} (\texttt{TsallisInf}), using $\alpha=1/2$ (it seems to be the most efficient of the algorithms described in the article).
    It is based on the online mirror descent algorithm with a Tsallis entropy regularizer, and it is anytime.
    It was also proven to obtain good ``best of both world'' performances.
    Empirically, we were unable to find any problem were it performs as well as \UCB{} (or any other efficient algorithm), and we are confident that our implementation is correct\footnote{~Despite a serious amount of time spent on this implementation, maybe it has some bug which explains the poor empirical performance obtained by \textsc{Tsallis-Inf} in our simulations. Exploring in more details this kind of algorithms is very interesting, as algorithms based on online mirror descent make a rich connection between multi-armed bandit and online convex optimization \cite{Hazan2016introduction}, and a short-term future work in \SMPyBandits{} will be to explore different values of $\alpha$ for Tsallis entropy regularization, or other families of regularization.}.
    \textsc{Tsallis-Inf} is also slower than \UCB{} (about as slow as \KLUCBswitch), and costs an-order-of-magnitude more memory.

@@

% \textbf{Effect of the number of jobs.}
% %
% As long as the number of jobs (\texttt{N\_JOBS} here) is less then or equal to the number of physical cores in the CPU of the computer, the final speed-up in terms of total computation runtime is almost optimal.
% %  dividing the running time by \texttt{N\_JOBS}.
% But jobs are implemented as threads, so the speed-up cannot be more than the number of cores, and using for instance $20$ jobs on $4$-cores for the $20$ repetitions is sub-optimal, as the CPU will essentially spend all its time (and memory) managing the different jobs, and not actually doing the simulations.
% Using the above example, we illustrate the effect of using multi-jobs and multi-cores on the time efficiency of simulations using SMPyBandits. We consider three values of \texttt{N\_JOBS}, $1$ to use only one core and one job, $4$ to use all the $4$ cores of my $i5$ Intel CPU, and $100$ jobs.
% %
% We give in Table~\ref{table:3:speedUpTimeParallelComputations} an example of running time of an experiment with $T=10000$, and different number of repetitions and number of jobs.
% These three experiments correspond to the three lines of Code Example~\ref{lst:3:runOneCoreOrMore} shown above.
% %
% The results of Table~\ref{table:3:speedUpTimeParallelComputations} clearly illustrate that using more jobs than the number of CPU is sub-optimal, and that as soon as the number of repetitions is large enough, using one job by available CPU core (\ie, here $4$ jobs) gives a significant speed-up time.
% Due to the cost of orchestrating the different jobs, and memory exchanges at the end of each repetition, the parallel version is \emph{not} $4$ times faster, but empirically we always found it to be $2$ to $3.5$ times faster.
% %
% Similar conclusions can be drawn from Figure~\ref{fig:3:analyze_speedup_as_nb_of_jobs}, which reports the results of the same experiment on a machine with $n_{\text{cores}}=12$ CPU cores.
% More details are included in the documentation page
% \href{https://smpybandits.github.io/About_parallel_computations.html}{\texttt{SMPyBandits.github.io/About\_parallel\_computations.html}}

@@

% % % Explain why I didn't try more on parallelisation (eg on Grid5000 or other large scale computer).
% % \paragraph{Approaches we did not try.}
% % %
% % The two other approaches we could have consider is parallel computations running on not multiple cores but multiple machines, in a computer cluster, or parallel computations running in a Graphical Processing Unit (GPU).

>>>>

\paragraph{References.}
%
The code for \SMPyBandits{} is hosted at \texttt{\href{https://GitHub.com/SMPyBandits/SMPyBandits/}{GitHub.com/SMPyBandits/SMPyBandits}}, its documentation is at \texttt{\href{https://SMPyBandits.GitHub.io/}{SMPyBandits.GitHub.io}}, and all the library is freely publicly released under the MIT open-source license.
This chapter is based on the article \cite{SMPyBanditsJMLR}.

@@

\paragraph{Simulation loop for single-player MAB.}
%
Any simulation library targeting single-player bandit problems must implement at least three components:
reward distributions, MAB algorithms, and a simulation loop that essentially looks like this.
% \begin{itemize}
    % \item
    First, initialize the MAB problem and one or more algorithms,
    % \item
    Then, for $t=1$ to $t=T$ (known beforehand), repeat the following block (for each algorithm). Ask algorithm $\cA$ her chosen arm $A(t)$, then sample a (random) reward $r(t)$ (\iid) from distribution $\nu_{A(t)}$, and finally feeds the observation $(A(t), r(t))$ to the algorithm.
    % \item
    At the end, compute the cumulated reward, the regret, then plot visualizations etc.
% \end{itemize}
%
Note that the second step should be repeated a large number of times (\eg, $N=100$), in order to study \emph{mean} regret and not only the regret in one single trajectory.
If one wants to compare algorithms on a same problem, it is possible to sample all the rewards $(Y_{k,t})_{k\in[K], t\in[T]}$ before-hand, and store them so that for each repetition of the simulation, the randomness from the environment (\ie, the rewards) has the same impact on all the algorithms (with the option \texttt{configuration["cache\_reward"] = True}).

@@

Any simulation library targeting multi-players bandit problems must implement at least another component:
% a collision model, and
a simulation loop that essentially looks like this.
% \begin{itemize}
    % \item
    First, initialize the MAB problem with $M$ players, and one or more cohorts of $M$ players (one player is one algorithm, usually $M$ times the same one),
    % \item
    For $t=1$ to $t=T$ (known beforehand), repeat the following block (for each cohort). Ask each player $\cA^j$ her chosen arm $A^j(t)$, then query the collision model to know which player will get a zero reward (for a collision) and which player will get a random reward from the environment.
    Then, sample (random) feedback $Y_{k,t}$ (\iid) from distributions $\nu_{k}$, and compute the rewards $r^j(t)$ from the random feedback using the collision model.
    Finally, feed the observation $(A^j(t), Y_{A^j(t),t}, r^j(t))$ to player $j$, for all the $M$ players,
    %
    The default collision model is the most widely studied in the literature, where a player encounters a collision (\ie, received a zero reward $r^j(t)=0$) if she is not the only one to have chosen an arm $k=A^j(t)$, otherwise $r^j(t)=Y_{A^j(t),t}$ if she is the only one playing this arm.
    % \item
    At the end, compute the accumulated reward, the regret, then plot visualizations etc.
% \end{itemize}

@@

gaussian_problem = MAB({'arm_type': Gaussian, 'params': means})
gaussian_problem.plotHistogram()  # display the histogram shown below
    \end{minted}
    \caption{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, and to plot a histogram of rewards, with \SMPyBandits.}
    % \captionof{listing}{Example of Python code to create Bernoulli and Gaussian arms, a MAB problem with $K=3$ arms, and to plot a histogram of rewards, with SMPyBandits. \label{lst:3:pythonCodeCreateProblem}}
    \label{lst:3:pythonCodeCreateProblem}
\end{listing}
\end{small}

@@

Simulations are easily executed, \eg, Code~\ref{lst:3:howToRunBasicLibrary} shows how to start $N=1000$ repetitions of a simple non-Bayesian Bernoulli-distributed problem, for $K=9$ arms, a horizon of $T=10000$ and on $4$ CPU.
It takes about $20$ min, on a $4$-core $64$-bit GNU/Linux laptop.
Environment variables (\texttt{N=1000} etc) in the command line are not required, but they are convenient.

@@

\paragraph{Travis CI.}
Since $2018$, we use the free web service provided by Travis CI (\href{https://travis-ci.org/}{\texttt{Travis-CI.org}}).
It allows to automatically run short numerical simulations after every commit,
in order to check that each modification on any part of the codebase does not break anything, as well as giving an up-to-date example of log files that shows online the results of different examples of experiments. The tests cover all the main models and almost all the algorithms implemented in \SMPyBandits, and it has been proven very useful to quickly find and fix new bugs.
For more details, see \href{https://travis-ci.org/SMPyBandits/SMPyBandits}{\texttt{Travis-CI.org/SMPyBandits/SMPyBandits}}.
%
Since its first use, the service did about $190$ builds, and about $30\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.travis.yml} file in \SMPyBandits{} main folder, and it runs numerical experiments with a short horizon (\eg, $T=100$) and a small number of repetitions (\ie, $N=4$), but covering all the different models implemented by \SMPyBandits{} (and even including some that are not covered in this chapter, like the Markov model, or the sparse multi-players model).
Builds typically run for $15$ minutes, and Travis CI have been proven to be very useful in our development process.

@@

    \item
In \cite{Besson2018DoublingTricks}, we used \SMPyBandits{} to illustrate and compare different "doubling trick" schemes.
\texttt{\href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{SMPyBandits.GitHub.io/DoublingTrick.html}}
% (see Appendix~\ref{app:2:DoublingTricks})
% In sequential learning, an algorithm is said to be ``anytime'' if it does not need to know the horizon $T$ of the experiments. A well-known trick for transforming any ``non-anytime'' algorithm to an ``anytime'' variant is the ``Doubling Trick'': start with a horizon $T_0\in\mathbb{N}^*$, and when $t > T_i$, use $T_{i+1} = 2 T_i$. We studied two generic sequences of growing horizons (geometric and exponential), and we proved two theorems that generalized previous results. A geometric sequence suffices to keep minimax regret bounds (in $R_T = \mathcal{O}(\sqrt{T})$), with a constant multiplicative loss $\ell \leq 4$, but cannot be used to keep a logarithmic regret bound (in $R_T = \mathcal{O}(\log(T))$). And an exponential sequence can be used to keep logarithmic bounds, with a constant multiplicative loss also $\ell \leq 4$ in the usual setting. It is still an open question to know if a well-tuned exponential sequence can keep minimax bounds, or "weak" minimax bounds (in $R_T = \mathcal{O}(\sqrt{T \log(T)})$).

@@

    \item
    % Algorithm 13 is
    Anytime variant of \KLUCBswitch{} from \cite{GarivierHadiji2018}
    (\texttt{klUCBswitchAnytime}),
    is a very recent variant of \KLUCB{} \cite{KLUCBJournal}.
    It mimics the \KLUCB{} algorithm but uses a much more complicated function to compute the upper confidence bounds, and uses more storage.
    It is anytime, and was proven to obtain good ``best of both world'' performances, meaning that it achieves an asymptotically optimal $\cO(\log(T))$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.
    Empirically, it usually outperforms (slightly) \klUCB{} in terms of regret, and costs about the same memory, but it is slower.

    \item
    % Algorithm 14 is
    \textsc{Tsallis-Inf} from \cite{Zimmert2018} (\texttt{TsallisInf}), using $\alpha=1/2$ (it seems to be the most efficient of the algorithms described in the article).
    It is based on the online mirror descent algorithm with a Tsallis entropy regularizer, and it is anytime.
    It was also proven to obtain good ``best of both world'' performances.
    Empirically, we were unable to find any problem where it performs as well as \UCB{} (or any other efficient algorithm), and we are confident that our implementation is correct\footnote{~Despite a serious amount of time spent on this implementation, maybe it has some bug which explains the poor empirical performance obtained by \textsc{Tsallis-Inf} in our simulations. Exploring in more details this kind of algorithms is very interesting, as algorithms based on online mirror descent make a rich connection between multi-armed bandit and online convex optimization \cite{Hazan2016introduction}, and a short-term future work in \SMPyBandits{} will be to explore different values of $\alpha$ for Tsallis entropy regularization, or other families of regularization.}.
    \textsc{Tsallis-Inf} is also slower than \UCB{} (about as slow as \KLUCBswitch), and costs an-order-of-magnitude more memory.

@@

% \textbf{Effect of the number of jobs.}
% %
% As long as the number of jobs (\texttt{N\_JOBS} here) is less than or equal to the number of physical cores in the CPU of the computer, the final speed-up in terms of total computation runtime is almost optimal.
% %  dividing the running time by \texttt{N\_JOBS}.
% But jobs are implemented as threads, so the speed-up cannot be more than the number of cores, and using for instance $20$ jobs on $4$-cores for the $20$ repetitions is sub-optimal, as the CPU will essentially spend all its time (and memory) managing the different jobs, and not actually doing the simulations.
% Using the above example, we illustrate the effect of using multi-jobs and multi-cores on the time efficiency of simulations using SMPyBandits. We consider three values of \texttt{N\_JOBS}, $1$ to use only one core and one job, $4$ to use all the $4$ cores of my $i5$ Intel CPU, and $100$ jobs.
% %
% We give in Table~\ref{table:3:speedUpTimeParallelComputations} an example of running time of an experiment with $T=10000$, and different number of repetitions and number of jobs.
% These three experiments correspond to the three lines of Code Example~\ref{lst:3:runOneCoreOrMore} shown above.
% %
% The results of Table~\ref{table:3:speedUpTimeParallelComputations} clearly illustrate that using more jobs than the number of CPU is sub-optimal, and that as soon as the number of repetitions is large enough, using one job by available CPU core (\ie, here $4$ jobs) gives a significant speed-up time.
% Due to the cost of orchestrating the different jobs, and memory exchanges at the end of each repetition, the parallel version is \emph{not} $4$ times faster, but empirically we always found it to be $2$ to $3.5$ times faster.
% %
% Similar conclusions can be drawn from Figure~\ref{fig:3:analyze_speedup_as_nb_of_jobs}, which reports the results of the same experiment on a machine with $n_{\text{cores}}=12$ CPU cores.
% More details are included in the documentation page
% \href{https://smpybandits.github.io/About_parallel_computations.html}{\texttt{SMPyBandits.github.io/About\_parallel\_computations.html}}

@@

% % % Explain why I didn't try more on parallelisation (eg on Grid5000 or other large scale computer).
% % \paragraph{Approaches we did not try.}
% % %
% % The two other approaches we could have considered is parallel computations running on not multiple cores but multiple machines, in a computer cluster, or parallel computations running in a Graphical Processing Unit (GPU).

### 2019-07-10 2-Chapters/5-Chapter/chapter5.tex
Vérifications grâce à emccabedj.ucc.asn.au/checktex.html, avant intégration des commentaires d'Emilie sur ma conclusion

We consider a bandit problem with $K=9$ arms, of means $0.1,\dots,0.9$, and three different cases of $M=3,6,9$ players, for $100$ independent repetitions and an horizon of $T=10000$.
As before, we include the centralized multiple-play \klUCB{} as an unachievably efficient baseline, the \Selfish-\klUCB{} algorithm as an heuristic which does not require to know $M$.
Then we compare the \RhoRand, \RandTopM{} and \MCTopM{} algorithms, using \klUCB, which know $M$ beforehand, with their extensions implementing the same algorithm as \rhoRandEst, to estimate $M$ on the fly.

>>>>

We consider a bandit problem with $K=9$ arms, of means $0.1,\dots,0.9$, and three different cases of $M=3,6,9$ players, for $100$ independent repetitions and a horizon of $T=10000$.
As before, we include the centralized multiple-play \klUCB{} as an unachievably efficient baseline, the \Selfish-\klUCB{} algorithm as an heuristic which does not require to know $M$.
Then we compare the \RhoRand, \RandTopM{} and \MCTopM{} algorithms, using \klUCB, which know $M$ beforehand, with their extensions implementing the same algorithm as \rhoRandEst, to estimate $M$ on the fly.
